`r params$doc_title`

### 2022-11-20 scripts/MSc.Rmd
finalized plot 1 grid (1x2)+(1x4)

library(dplyr)
library(purrr)
library(tidyr)
library(stringr)
library(tibble)
library(ggplot2)
library(ggthemes)
library(scales)
library(ggthemes)
#library(biomaRt)  # different script
library(kableExtra)
library(MendelianRandomization)
library(TwoSampleMR)
library(mr.raps)
library(MRMix)
library(MRPRESSO)
library(penalized)
library(conflicted)
source("MR_lasso.R")  # Slob&Burgess 2020
conflict_prefer("select", "dplyr")
conflict_prefer("filter", "dplyr")
```

@@

```{r fig.height=10, fig.width=14, warning=FALSE}
ggpubr::ggarrange(fig01b.update, fig02.update, 
                  figure01_EFFECT_SIZE_strong_VARIANTS_common, figure01_EFFECT_SIZE_strong_VARIANTS_rare,
                  figure01_EFFECT_SIZE_weak_VARIANTS_common, figure01_EFFECT_SIZE_weak_VARIANTS_rare, 
                  ncol=2, nrow=3)
```

>>>>

library(dplyr)
library(purrr)
library(tidyr)
library(stringr)
library(tibble)
library(ggplot2)
library(ggthemes)
library(ggpubr)
library(scales)
#library(biomaRt)  # different script
library(kableExtra)
library(MendelianRandomization)
library(TwoSampleMR)
library(mr.raps)
library(MRMix)
library(MRPRESSO)
library(penalized)
library(conflicted)
source("MR_lasso.R")  # Slob&Burgess 2020
conflict_prefer("select", "dplyr")
conflict_prefer("filter", "dplyr")
```

@@

```{r fig.height=10, fig.width=14, warning=FALSE}
fig01b.update + 
  labs(title= "Figure 1", caption = "") -> fig01b.update.arrange

fig02.update+
  labs(title= "Genetic architectures", subtitle="", caption = "") -> fig02.update.arrange

figure01_EFFECT_SIZE_strong_VARIANTS_common+
  labs(title= "", caption = "") -> figure01_EFFECT_SIZE_strong_VARIANTS_common.arrange

figure01_EFFECT_SIZE_strong_VARIANTS_rare+
  labs(title= "", caption = "") -> figure01_EFFECT_SIZE_strong_VARIANTS_rare.arrange

figure01_EFFECT_SIZE_weak_VARIANTS_common+
  labs(title= "", caption = "") -> figure01_EFFECT_SIZE_weak_VARIANTS_common.arrange

figure01_EFFECT_SIZE_weak_VARIANTS_rare+
  labs(title= "", caption = "") -> figure01_EFFECT_SIZE_weak_VARIANTS_rare.arrange

ggpubr::ggarrange(fig01b.update.arrange, fig02.update.arrange,
                  gfigure01_EFFECT_SIZE_strong_VARIANTS_common.arrange, figure01_EFFECT_SIZE_strong_VARIANTS_rare.arrange,
                  figure01_EFFECT_SIZE_weak_VARIANTS_common.arrange, figure01_EFFECT_SIZE_weak_VARIANTS_rare.arrange, 
                  ncol=2, nrow=3, 
                  heights = c(2, 1.5, 1.5),
                  legend = "bottom", common.legend = TRUE, align = "hv"
                  ) -> final_plot1.arrange

figure01_EFFECT_SIZE_strong_VARIANTS_rare.arrange+
  scale_y_continuous(name="", sec.axis = sec_axis(~./scale_factor, name=""), limits = c(0,2))

    scale_y_continuous(
      # Features of the first axis
      name = "% variance explained by IVs",
      # Add a second axis and specify its features
      sec.axis = sec_axis(~./scale_factor, name="Number of IVs"),
      limits = c(0,2)
    ) +

ggpubr::ggarrange(ggarrange(fig01b.update.arrange, fig02.update.arrange, ncol=2, labels = c("A", "B"), legend = "none", align = "hv"),
                  ggarrange(figure01_EFFECT_SIZE_strong_VARIANTS_common.arrange, figure01_EFFECT_SIZE_strong_VARIANTS_rare.arrange,
                  figure01_EFFECT_SIZE_weak_VARIANTS_common.arrange, figure01_EFFECT_SIZE_weak_VARIANTS_rare.arrange, 
                  ncol=4, labels = c("C", "D", "E", "F"), legend="bottom", common.legend = TRUE),
                  nrow=2
                  #heights = c(2, 1.5, 1.5),
                  #legend = "bottom", common.legend = TRUE, align = "hv"
                  ) -> final_plot1.arrange2

final_plot1.arrange
final_plot1.arrange2

filename_final_plot1 <- paste0("../output/plots/", Sys.Date(), "_final_plot1.arrange.png")
filename_final_plot1b <- paste0("../output/plots/", Sys.Date(), "_final_plot1b.arrange.png")

ggsave(filename = filename_final_plot1, plot = final_plot1.arrange, 
         width = 14, height = 10, 
         units = "in"  # default
         )
ggsave(filename = filename_final_plot1b, plot = final_plot1.arrange2, 
         width = 14, height = 10, 
         units = "in"  # default
         )
